Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-25 paper.tex
fixed typo in 2
improve weak bisim statement

@@

\begin{definition}[$s \approx^{*} s$]
Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
that
\[
s_1 \approx s_2'
\;\text{and}\;
\judgeDreduceTrans{s_2}{s_2'}
\]
\end{definition}

@@

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
  \label{thm:SD-bisim}
  Assume $C$ implements Lazy D Cast ADT
  and $C$ is a monoid
  and $cast(T,l,T)=id(T)$,
  $s_{1} \in \text{\effCEK{C}}$,
  $s_{2} \in \text{\ineffCEKD}$,
  $s_{1} \approx s_{2}$,
\begin{enumerate}
  \item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
    then $\judgeDreduce{s_2}{s_4}$ 
    and  $s_3 \approx^{*} s_4$
    for some $s_4$
  \item If $\judgeDreduce{s_2}{s_4}$
    then $\judgeSreduce{C}{s_1}{s_3}$ 
    and  $s_3 \approx^{*} s_4$
    for some $s_3$
\end{enumerate}
  Or diagrammatically, 
  \[\begin{array}{clclc}
  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
  \rotatebox[origin=c]{90}{$\approx$} 
  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
  s_{2} & 
  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
  \end{array}\]
\end{lemma}
\begin{proof}
  Part (1) and (2) follow from the definition of $s \approx s$.
  Part (3) and (4) are more interesting. 
  By the definition of $s \approx s$, it is straightforward to prove 
  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
  So we can prove two parts together by showing that 
  \[
  \text{if}\; s_{1} \approx s_{2}
  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
  \;\text{and}\;\judgeDreduce{s_2}{s_4}
  \;\text{then}\; s_3 \approx^{*} s_4.
  \]
  To put it another way, our goal is to proving 
  one reduction step in \effCEK{C} corresponds to
  one or more steps in \ineffCEKD.  
  Although there are many cases, the general idea is the same.
  Consider
  \[
  \sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
    wrap(\kOOcar{\kappa})
  }
  \approx
  \sOOreturn{v_2}{\kOOcar{\kappa}}
  \]

>>>>

\newcommand{\judgeDreducePlus}[2]{#1 \longmapsto_{\mathcal{D}}^{+} #2}

@@

\begin{definition}[$s \approx^{*} s$]
Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
that
\[
\judgeDreduceTrans{s_2}{s_2'}
\;\text{and}\;
s_1 \approx s_2'
\]
\end{definition}

@@

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
  \label{thm:SD-bisim}
  Assume $C$ implements Lazy D Cast ADT
  and $C$ is a monoid
  and $cast(T,l,T)=id(T)$,
  $s_{1} \in \text{\effCEK{C}}$,
  $s_{2} \in \text{\ineffCEKD}$,
  $s_{1} \approx s_{2}$,
\begin{enumerate}
  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
    then $\judgeDreduce{s_2}{s_4}$ 
    and  $s_3 \approx^{*} s_4$
    for some $s_4$
  \item If $\judgeDreduce{s_2}{s_4}$
    then $\judgeSreduce{C}{s_1}{s_3}$ 
    and  $s_3 \approx^{*} s_4$
    for some $s_3$
\end{enumerate}
{\color{red}
  Jeremy's attempt to reformulate in a more standard way that
  remains equivalent:
\begin{enumerate}
\item If $\judgeSreduce{C}{s_1}{s_3}$ then
  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
\item If $\judgeDreduce{s_2}{s_4}$ then
  $\judgeSreduce{C}{s_1}{s_3}$,
  $\judgeDreduceTrans{s_2}{s_5}$, and
   $s_3 \approx s_5$ for some $s_3$ and $s_5$.
\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
\end{enumerate}
}
Or diagrammatically, 
  \[\begin{array}{clclc}
  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
  \rotatebox[origin=c]{90}{$\approx$} 
  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
  s_{2} & 
  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
  \end{array}\]
\end{lemma}
\begin{proof}
  Part (1) follow from the definition of $s \approx s$.
  Part (2) and (3) are more interesting. 
  By the definition of $s \approx s$, it is straightforward to prove 
  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
  So we can prove two parts together by showing that 
  \[
  \text{if}\; s_{1} \approx s_{2}
  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
  \;\text{and}\;\judgeDreduce{s_2}{s_4}
  \;\text{then}\; s_3 \approx^{*} s_4.
  \]
  To put it another way, our goal is to proving 
  one reduction step in \effCEK{C} corresponds to
  one or more steps in \ineffCEKD.  
  Although there are many cases, the general idea is the same.
  Consider
  \[
  \sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
    wrap(\kOOcar{\kappa})
  }
  \approx
  \sOOreturn{v_2}{\kOOcar{\kappa}}
  \]
